Numerical modelling of the Cordilleran ice sheet

### 2014-07-19 kappa.tex
Various figure adjustements.

% Finally to not include graphics
%\renewcommand{\includegraphics}[2][,]{}
%\renewcommand{\subgraphics}[3][,]{}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-timeseries}
  \caption{Palaeo-climate records of the last 800\,ka.
           \textbf{(a)} Benthic oxygen isotope (\chem{\delta^{18}O}) record
           from a compilation of globally-distributed deep sea sediment cores
           \citep{Lisiecki.Raymo.2005}. Higher \chem{\delta^{18}O} values
           correspond to periods of lower temperatures \citep{Emiliani.1955}
           or lower global sea level, and thus higher ice volume stored in
           glaciers and ice sheets on land \citep{Shackleton.1967}.
           \textbf{(b)} Temperature anomalies ($\Delta T$) reconstructed from a
           central Antarctic ice core \citep[EPICA Dome~C,][]{Jouzel.etal.2007}.
           The grey bands indicate the approximate time span of the last
           glacial period of 110 to 10\,ka.
           \todo{Put nicer blue and red colours.}}
  \label{fig:paleo-timeseries}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present \citep{Patterson.Kelso.2014}, and
           \textbf{(b)} during the last glacial maximum
           \citep{Ehlers.Gibbard.2007}.
           \todo{Make these globes look a little bigger. Add (a) and (b).}}
  \label{fig:paleo-glaciation}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-interfaces}
  \caption{Model interfaces in PISM. From \citet{PISM-authors.2014}.
           \todo{This is directly from the PISM manual. I may redraw it here
                 if I have the time.}}
  \label{fig:model-interfaces}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{model-variables}
  \caption{Sketch of notations used for the main variables of the ice sheet
           model. A particle of ice is moving at velocity $\vv$, under the
           balance of stresses $\CST$ and gravity $\vect{g}$.}
  \label{fig:model-variables}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-siassa}
  \caption{Shallow Ice Approximation (SIA) and Shallow Shelf Approximation
           (SSA) velocities in PISM. From \citet{Winkelmann.etal.2011}.
           \todo{Redraw in LaTeX in the same style as
                 \cref{fig:model-variables}.}}
  \label{fig:model-siassa}
\end{figure}

@@

\begin{figure*}
  \centering
  \vspace{-16mm}
  \makebox[0pt]{
  \begin{minipage}[t]{112.5mm}\vspace{0pt}
    \includegraphics{plot-lgm}
  \end{minipage}
  \hspace{1cm}
  \begin{minipage}[t]{47.5mm}\vspace{0pt}
    \caption{Constant-climate simulation of the LGM Cordilleran ice sheet using
             an horizontal resolution of 3\,km. Modelled basal topography,
             cold-based areas (hatches), surface topography (100\,m contours)
             and surface velocities. The simulation is forced by atmospheric
             fields from the NARR \citep{Mesinger.etal.2006} and a temperature
             depression of 7\,\degC, using the set-up described in \CCLI. There
             are several issues with this run. First, all east-facing margins
             are too extensive as compared to available reconstructions.
             Second, marine advance on the Pacific Shelf is too restrictive,
             most notably in the south-western corner where the Puget and Juan
             de Fuca lobes are missing. Third, en-glacial temperatures are
             anomalously low due to brutal application of cold climate
             condition to ice-free bedrock at the inception of the run.
             \todo{Add black frame, and maybe the LGM outline from Dyke?}}
    \label{fig:plot-lgm}
  \end{minipage}
  }
  \vspace{-16mm}
\end{figure*}

>>>>

% Some general low-priority todos
% -- switch to kappa.cls
% -- incorporate figs as pdf, rasterize heavy elements
% -- use latex in matplotlib figures
% -- homogeneize subfig label fonts
% -- add software references
% -- redraw PISM interface

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-timeseries}
  \caption{Palaeo-climate records of the last 800\,ka.
           \textbf{(a)} Benthic oxygen isotope (\chem{\delta^{18}O}) record
           from a compilation of globally-distributed deep sea sediment cores
           \citep{Lisiecki.Raymo.2005}. Higher \chem{\delta^{18}O} values
           correspond to periods of lower temperatures \citep{Emiliani.1955}
           or lower global sea level, and thus higher ice volume stored in
           glaciers and ice sheets on land \citep{Shackleton.1967}.
           \textbf{(b)} Temperature anomalies ($\Delta T$) reconstructed from a
           central Antarctic ice core \citep[EPICA Dome~C,][]{Jouzel.etal.2007}.
           The grey bands indicate the approximate time span of the last
           glacial period of 110 to 10\,ka.}
  \label{fig:paleo-timeseries}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present \citep{Patterson.Kelso.2014}, and
           \textbf{(b)} during the last glacial maximum
           \citep{Ehlers.Gibbard.2007}.}
  \label{fig:paleo-glaciation}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=85mm]{model-interfaces}
  \caption{PISM is a numerical model for ice and bedrock physics. Processes
           occurring at the interface with the atmosphere and the ocean, that
           are progressive transitions in nature, are parametrised along
           well-defined boundaries in the model.
           From \citet{PISM-authors.2014}.}
  \label{fig:model-interfaces}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{model-variables}
  \caption{Sketch of notations used for the main variables of the ice sheet
           model. An infinitesimal ice parcel is moving at velocity $\vv$,
           under the balance of stresses $\CST$ and gravity $\vect{g}$.}
  \label{fig:model-variables}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-siassa}
  \caption{Combination of Shallow Ice Approximation (SIA) and Shallow Shelf
           Approximation (SSA) velocities in PISM, assuring a smooth transition
           between shear-dominant and longitudinal stress regimes. After
           \citet[Fig.~1]{Winkelmann.etal.2011}. Not to scale.}
  \label{fig:model-siassa}
\end{figure}

@@

\begin{figure*}
  \centering
  \vspace{-16mm}
  \makebox[0pt]{
  \begin{minipage}[t]{112.5mm}\vspace{0pt}
    \includegraphics{plot-lgm}
  \end{minipage}
  \hspace{1cm}
  \begin{minipage}[t]{47.5mm}\vspace{0pt}
    \caption{Constant-climate simulation of the LGM Cordilleran ice sheet using
             an horizontal resolution of 3\,km. The map depicts modelled basal
             topography, cold-based areas (hatches), surface topography (100\,m
             contours) and surface velocities, and a reconstruction of the
             approximate ice sheet margin at 16.8\,cal\,ka from compiled
             geomorphological evidence \citep[red contour;][]{Dyke.2004}.
             The simulation is forced by atmospheric
             fields from the NARR \citep{Mesinger.etal.2006} and a temperature
             depression of 7\,\degC, using the set-up described in \CCLI. There
             are several issues with this run. First, all east-facing margins
             are too extensive as compared to available reconstructions.
             Second, marine advance on the Pacific Shelf is too restrictive,
             most notably in the south-western corner where the Puget and Juan
             de Fuca lobes are missing. Third, en-glacial temperatures are
             anomalously low due to brutal application of cold climate
             condition to ice-free bedrock at the inception of the run.}
    \label{fig:plot-lgm}
  \end{minipage}
  }
  \vspace{-16mm}
\end{figure*}
